Conflict-Free Vertex Coloring Of Planar Graphs

### 2017-05-01 paper/paper.tex
Last minute changes

It is often desirable and necessary to use approximation algorithms, called heuristics, to solve complex problems like the VCP and the CFCP. In our case, heuristics are polynomial-time algorithms that give good, but not optimal, solutions to our optimization problems. A polynomial-time approximation scheme (PTAS) is any polynomial-time approximation algorithm that takes an instance of an optimization problem and a parameter $\epsilon > 0$ and produces a solution that is within a factor $(1 + \epsilon)$ (for minimization problems) of being optimal.

@@

\begin{theorem} \label{thm:four}
Every loopless planar graph admits a vertex coloring with at most four distinct colors.
\end{theorem}

@@

\begin{theorem} \label{thm:four-cf}
Every loopless planar graph admits a conflict-free coloring with at most three distinct colors.
\end{theorem}

>>>>

It is often desirable and necessary to use approximation algorithms, known as heuristics, to solve complex problems like the VCP and the CFCP. In our case, heuristics are polynomial-time algorithms that give good, but not optimal, solutions to our optimization problems. A polynomial-time approximation scheme (PTAS) is any polynomial-time approximation algorithm that takes an instance of an optimization problem and a parameter $\epsilon > 0$ and produces a solution that is within a factor $(1 + \epsilon)$ (for minimization problems) of being optimal.

@@

\begin{theorem} \label{thm:four}
Every loopless planar graph admits a proper vertex coloring with at most four distinct colors.
\end{theorem}

@@

\begin{theorem} \label{thm:four-cf}
Every loopless planar graph admits a valid conflict-free coloring with at most three distinct colors.
\end{theorem}
